Descriptive_Stats

### 2023-07-26 Code/GLMM.Rmd
Changed blue curve and smoothed exact=True

  sbase <- summary(base)
  x <- simfit(model)
  print(mean(x < RxnTime))
  #print(quantile(x, prob = c(0.00001, 0.0001, 0.0005, 0.001)))
  ## compare with and without random effect
  plot(density(x))  # with random effects
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.22, add = TRUE, col = "blue")  # fixed effect only
}
```

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model
```{r}
#7
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.1)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.1)
```

@@

This next code section replicates the code above but the various simulation
functions are meant for one random effect instead of two.
```{r}
#11
library(lme4)
set.seed(1)
sim_one_effect_time <- function(model, base, RxnTime){
    simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    ## mu <- exp(coef(model)$Year[,]) ## using fitted random effects only
    z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
    mu <- exp(fixef(model) + z)
    shape <- 1 / vc$vcov[2]
    x <- rgamma(n, shape = shape, scale = mu / shape)
    x
    }
  sbase <- summary(base)
  #print(sbase)
  x <- simfit(model)
  print(mean(x < RxnTime))
  ## compare with and without random effect
  plot(density(x)) # with random effect
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.22, add = TRUE, col = "blue") # fixed effect only
}
```

>>>>

  sbase <- summary(base)
  x <- simfit(model)
  print(mean(x < RxnTime))
  #print(quantile(x, prob = c(0.00001, 0.0001, 0.0005, 0.001)))
  ## compare with and without random effect
  plot(density(x))  # with random effects
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.25, add = TRUE, col = "blue")  # fixed effect only
}
```

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model
```{r}
#7
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.1)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.1)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.1)
```
```{r}
sim_two_effect_time(men_old_finals_two_effect_gamma_log, men_old_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_finals_two_effect_gamma_log, men_finals_one_gamma_log, 0.08)
sim_two_effect_time(men_old_pooled_two_effect_gamma_log, men_old_pooled_one_gamma_log, 0.08)
sim_two_effect_time(men_pooled_two_effect_gamma_log, men_pooled_one_gamma_log, 0.08)
```

@@

This next code section replicates the code above but the various simulation
functions are meant for one random effect instead of two.
```{r}
#11
library(lme4)
set.seed(1)
sim_one_effect_time <- function(model, base, RxnTime){
    simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    ## mu <- exp(coef(model)$Year[,]) ## using fitted random effects only
    z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
    mu <- exp(fixef(model) + z)
    shape <- 1 / vc$vcov[2]
    x <- rgamma(n, shape = shape, scale = mu / shape)
    x
    }
  sbase <- summary(base)
  #print(sbase)
  x <- simfit(model)
  print(mean(x < RxnTime))
  ## compare with and without random effect
  plot(density(x)) # with random effect
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.25, add = TRUE, col = "blue") # fixed effect only
}
```

### 2023-07-26 Code/RankComparison.Rmd
Changed blue curve and smoothed exact=True

clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations,
                alternative = "greater", method = "ds",
                exact = TRUE, B = 10000)
```

@@

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                alternative = "greater", method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                alternative = "greater", method = "ds",
                exact = TRUE, B = 10000)
```

>>>>

clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations,
                alternative = "greater", method = "ds",
                exact = TRUE, B = 10000)
```
```{r}
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, method = "ds",
                exact = TRUE, B = 10000)
```

@@

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = comp,
                method = "ds",
                exact = TRUE, B = 10000)
```
